\begin{thebibliography}{1}

\bibitem{mqttv311}
A. Banks and R. Gupta
\textit{MQTT Version 3.1.1 Plus Errata 01},
OASIS Standard Incorporating Approved Errata 01, 10 December 2015.
Available: \url{http://docs.oasis-open.org/mqtt/mqtt/v3.1.1/errata01/os/mqtt-v3.1.1-errata01-os-complete.html}.
Latest version: \url{http://docs.oasis-open.org/mqtt/mqtt/v3.1.1/mqtt-v3.1.1.html}.

\bibitem{iot_survey} 
A. Al-Fuqaha, M. Guizani, M. Mohammadi, M. Aledhari, and M. Ayyash, 
"Internet of Things: A Survey on Enabling Technologies, Protocols, and Applications,''
\textit{IEEE Communications Surveys \& Tutorials}, 
vol. 17, no. 4, pp. 2347--2376, 2015.

\bibitem{mosquitto} 
R. A. Light, 
"Mosquitto: server and client implementation of the MQTT protocol,''
\textit{Journal of Open Source Software}, 
vol. 2, no. 13, p. 265, 2017.

\bibitem{ref_6} 
M. B. Yassein, W. Q. Al-Sarayrah, and A. Al-Zoubi, 
"Performance Analysis of MQTT Protocol in IoT,'' 
in \textit{Proc. 2023 IEEE International Conference on Engineering \& MIS (ICEMIS)}, 
Istanbul, Turkey, 2023, 
pp. 1--6.


\bibitem{ref_7} 
S. K. Prasad, J. Rachna, and A. Khalaf, 
"Performance Evaluation of MQTT Protocol in Internet of Things,'' 
\textit{Telecommunications and Radio Engineering}, 
vol. 82, no. 8, pp. 45--58, 2023.

\bibitem{ref_8} 
T. T. D. Nguyen, G. Armitage, and P. Branch, 
"Performance Impact Analysis of Securing MQTT Using TLS,'' 
in \textit{Proc. 2021 ACM/SPEC International Conference on Performance Engineering}, 
2021, pp. 1--12.

\bibitem{ref_9} 
A. F. Gentile, D. Macrì, D. L. Carnì, E. Greco, and F. Lamonaca, 
"A Network Performance Analysis of MQTT Security Protocols with Constrained Hardware in the Dark Net for DMS,'' 
\textit{Applied Sciences}, 
vol. 14, no. 18, p. 8501, 2024.

\bibitem{ref_10} 
J. Silva, P. Pedreiras, and L. Almeida, 
"A Scalable Real-Time SDN-Based MQTT Framework for Industrial Applications,'' 
\textit{IEEE Open Journal of the Industrial Electronics Society}, 
vol. 5, pp. 102--115, 2024.

\bibitem{ref_11} 
F. Tao, H. Zhang, A. Liu, and A. Y. C. Nee, 
"Digital Twin in Industry: State-of-the-Art,'' 
\textit{IEEE Transactions on Industrial Informatics}, 
vol. 15, no. 4, pp. 2405--2415, Apr. 2019.

\bibitem{ref_12} 
T. H. Nguyen, Z. J. Wang, and V. C. M. Leung, 
"Digital Twin Empowered Industrial IoT Based on Credibility-Weighted Swarm Learning,'' 
\textit{IEEE Transactions on Industrial Informatics}, 
vol. 20, no. 1, pp. 567--578, Jan. 2024.

\bibitem{ref_13} 
M. A. Al-Garadi, A. Mohamed, A. Al-Ali, X. Du, and M. Guizani, 
"A Survey of Machine and Deep Learning Methods for Internet of Things (IoT) Security,
'' \textit{IEEE Communications Surveys \& Tutorials}, 
vol. 22, no. 3, pp. 1646--1685, 2020.

\bibitem{ref_14} 
Y. Han, W. Zhang, Z. Niu, and S. Zhou, 
"Machine and Deep Learning for Digital Twin Networks: A Survey,'' 
\textit{IEEE Internet of Things Journal}, 
vol. 11, no. 2, pp. 1234--1256, Jan. 2024.

\bibitem{ref_15} 
L. U. Khan, W. Saad, D. Niyato, Z. Han, and C. S. Hong, 
"Digital-Twin-Enabled 6G: Vision, Architectural Trends, and Future Directions,'' 
\textit{IEEE Communications Surveys \& Tutorials}, 
vol. 24, no. 4, pp. 2234--2275, 2022.

\bibitem{ref_16} 
T. R. Henderson, M. Lacage, G. F. Riley, C. Dowell, and J. Kopena, 
"Network simulations with the ns-3 simulator,'' 
\textit{SIGCOMM Demonstration}, 
vol. 14, no. 14, p. 527, 2008.

\bibitem{ref_17}
M. Augusto, "MQTT for NS-3," Technical Report, Jan. 2023.
Last accessed on Nov. 20, 2025. [Online]. Available: \url{https://sourceforge.net/projects/mqttforns3/}.

\bibitem{ref_18}
M. A. Salimee, M. A. Pasha, and S. Masud,
"NS-3 Based Open-Source Implementation of MQTT Protocol for Smart Building IoT Applications,"
in \textit{Proc. 2023 Int. Conf. Communication, Computing and Digital Systems (C-CODE)},
Islamabad, Pakistan, May 2023, pp. 1-6.
doi: 10.1109/C-CODE58145.2023.10139859.

\bibitem{ref_19} 
F. A. Alenizi and F. Al-Turjman, 
"A Survey on IoT Simulators: A Performance Comparison,'' 
\textit{IEEE Access}, 
vol. 11, pp. 12345--12360, 2023.

\bibitem{ref_20} 
R. Maldonado, A. Karstensen, G. Pocovi, and A. A. Esswein, 
"Comparing Wi-Fi 6 and 5G Downlink Performance for Industrial IoT,'' 
\textit{IEEE Access}, 
vol. 9, pp. 123456--123467, 2021.

\bibitem{ref_21} 
S. Deronne, T. R. Henderson, and S. Roy, 
"Validation of Wi-Fi Models in ns-3,'' 
in \textit{Proc. of the Workshop on ns-3 (WNS3)}, 
2019, pp. 1--8.

\bibitem{ref_22} 
5G-ACIA, 
"Integration of 5G with Time-Sensitive Networking for Industrial Communications,'' 
5G Alliance for Connected Industries and Automation, 
White Paper, 2021.

\end{thebibliography}

